Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-11 hamiltonian.tex
Add discussion notes

\section{Construction of the XZ Local Hamiltonian}
\label{sec:Hamiltonian}

\XW{highlight the different requirement from the normal Local Hamiltonian reduction; and highlight a bit about the solution idea}

In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian instance.

The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
\Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}

>>>>

\section{Construction of the X-Z Local Hamiltonian for $\SampBQP$}
\label{sec:Hamiltonian}

\def \Hin {H_{\mathrm{in}}}
\def \Hout {H_{\mathrm{out}}}
\def \Hprop {H_{\mathrm{prop}}}
\newcommand{\histpsi}[1]{\ket{\psi_{#1}^{\mathrm{hist}}}}

As we mentioned in this introduction, we will employ the circuit \emph{history} state in the original construction of the Local Hamiltonian problem~\cite{kitaev2002classical} to encode the circuit information for $\SampBQP$. 
However, there are distinct requirements between certifying the computation for $\BQP$ and $\SampBQP$ based on the history state.
For any quantum circuit $C$ on input $x$, the original construction for certifying $\BQP$\footnote{The original construction is for the purpose of certifying problems in QMA. We consider its simple restriction to problems inside BQP.} consists of three parts of local Hamiltonian $\Hin, \Hprop$, $\Hout$ where $\Hin$ is used to certify the initial input $x$, $\Hprop$ to certify the gate-by-gate evolution according to the circuit description, and $\Hout$ to certify the final output. 
In particular, the history state referring to quantum circuit $C$ on input $x$ is in the ground space of $\Hin$ and $\Hprop$. Note that $\BQP$ is a decision problem and its outcome (0/1) can be easily encoded into the energy $\Hout$ on the single output qubit. 
As a result, the outcome of $\BQP$ can simply be encoded by the \emph{ground energy} of $\Hin + \Hprop + \Hout$.

To deal with $\SampBQP$, we will still employ $\Hin$ and $\Hprop$ to certify the circuit's input and gate-by-gate evolution. However, in this case, we care about the entire final state of the circuit, rather than the energy on the output qubit. The history state is still in the ground space of $\Hin + \Hprop$.  
One approach to certify the entire final state encoded inside the history state is to make sure that the history state is the unique ground state of $\Hin + \Hprop$ and all other orthogonal states will have much higher energies. 
Namely, we need to construct some $\Hin'+ \Hprop'$ with the history state as the unique ground state and with a large \emph{spectral} gap between the ground energy and excited energies. 
This guarantees that any state with close-to-ground energy must also be close to the history state. 
We remark that this is a much stronger and different requirement from most local Hamiltonian constructions where the focus is on the ground energy. 
However, we show it can indeed be achieved by using the \emph{perturbation} technique 
developed in the local Hamiltonian literature (e.g.~\cite{kempe_kitaev_regev_2006}) for a different purpose.

%\XW{highlight the different requirement from the normal Local Hamiltonian reduction; and highlight a bit about the solution idea}

% In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian instance.
% The local Hamiltonian problem is $\QMA$-complete, which means it's $\BQP$-hard.
% Protocols to delegate $\BQP$ computations such as \cite{FOCS:Mahadev18a} \Ethan{Are there any more?} take advantage of this fact and require the prover to send the corresponding $\QMA$ certificate.
% We take a similar approach to delegate $\SampBQP$ computations; however, we need to extract more information from the certificates.
% Local Hamiltonians have been extensively studied in contexts of adiabatic quantum computations, so we will summarize known results from sources such as \cite{adiabatic}.
% \Ethan{This source was given to us by Yu-Ching; I haven't read it. Also I probably should cite more sources here.}

### 2020-04-11 qpip.tex
Add discussion notes

	Inputs:
	\begin{itemize}
		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon=\frac{1}{\poly(\lambda)}$ \Ethan{This feels strange... Neither $\forall\poly$ nor $\exists\poly$ feels right.}
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
		\item Let $T$ be the number of gates in $C$.
		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{21}\lambda^2}{\varepsilon^{31}}$ \Ethan{I think? Double check later} copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item\label{step:qpip1-verify} The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}\lambda}{\varepsilon^{14}}$, and $k\xleftarrow{\$}[M]\setminus I$. \hannote{$\xleftarrow{\$}$ ?} \Ethan{Sample randomly from. I thought it's standard notation}
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $z$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Y=\sum_{i\in I} y_i$. If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier outputs $(\Acc, z)$.
			Else, it outputs $(\Rej, \bot)$.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is simple to check that $\PiSamp$ runs in $\poly(n, \lambda)$ time. \Ethan{Right? Or just $\poly(\lambda)$?}
We now show its completeness and soundness.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and is computationally sound.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq\negl(\lambda).$$

	Now we show soundness.

	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier.

@@

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $M$-fold tensor products of identical copies of some states $\tau_j$.
	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{6T}{\varepsilon}\right)}{M-m}}
	\leq\frac{\varepsilon}{6}$$
	where $\sigma'_{\leq m+1}$ is the first $m+1$ registers of $\sigma'$.
	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
	$\Lambda_{m+1}$ measures the data register of $\rho_k$.

	For each $\tau_j$, we define the distribution $(d_j, z_j)$ to correspond to $\VSamp$'s output if it were to receive $\tau_j^{\otimes M}$ from $\PSampstar$, and define $z_{j, ideal}$ accordingly.
	We claim that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.
	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider the following two cases.

@@

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\frac{\varepsilon^2}{36}.$$
	which in turn implies a lower bound on the respective trace distance:
	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\varepsilon}{6}.$$
	Suppose $d_j=\Acc$, then $z_j$ would be the measurement on $\tau_j$'s data register,
	which is $\frac{\varepsilon}{6}$-close to that on $\ket{\psi_{C'(x)}}$.
	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has at least $1-\frac{\varepsilon}{6}$ probability to contain $C(x)$ due to the padding.
	So $z_j$ is $\frac{2\varepsilon}{6}$-close to $z_{ideal}$ when $d=\Acc$,
	which implies that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.

	Define $z_\rho$ to be the output distribution corresponding to if $\VSamp$ were to receive $\rho=\sum_j w_j\tau_j^{\otimes M}$ instead of $\sigma$ from the server,
	and define $z_{\rho, ideal}$ accordingly.
	We have $\norm{(d_\rho, z_\rho) - (d, z_{\rho, ideal})}_{TV} < \frac{2\varepsilon}{6}$ since the same is true for all components $\tau_j$.

	As $(d, z)$ is $\frac{\varepsilon}{6}$-close to $(d_\rho, z_\rho)$ for some $\rho$ by de Finetti's theorem and data processing inequality,
	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
	Hence we have $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
	The conclusion then follows from triangle inequality.
\end{prf}

>>>>

	Inputs:
	\begin{itemize}
		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon=\frac{1}{\poly(\lambda)}$ \Ethan{Just say between 0 and 1; specify poly lambda in thm statement}
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
		\item Let $T$ be the number of gates in $C$.
		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$. \Ethan{Cite previous theorem}
		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item Let $\cVGS$ be the verification algorithm for $H_{C'(x)}$ as defined in \Cref{AlgGroundStateCheck}.
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{21}\lambda^2}{\varepsilon^{31}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item\label{step:qpip1-verify} The verifier samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}\lambda}{\varepsilon^{14}}$, and $k\xleftarrow{\$}[M]\setminus I$. \hannote{$\xleftarrow{\$}$ ?} \Ethan{Sample randomly from. Will add it to preliminary section.}
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $z$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Y=\sum_{i\in I} y_i$. If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ is the constant specified in \Cref{cor:HamCheck}, then the verifier outputs $(\Acc, z)$.
			Else, it outputs $(\Rej, \bot)$.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is simple to check that $\VSamp$ runs in $\poly(n, \lambda, \frac{1}{\epsilon})$ time.
We now show its completeness and soundness.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and is statistically sound.
	\Ethan{Should also say $\lambda$ and $\varepsilon$ are inverse poly related. Or actually, maybe specify that in soundness dfn.}

	\Ethan{Might want to define verifier being efficient (poly-time) there too}
\end{thm}
\begin{prf}
	For completeness, notice $y_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) to get
	$$\Prob{Y>\frac{m}{2}-\varepsilon m}\leq\negl(\lambda).$$
	\Ethan{So its rejection chance is...}

	Now we show soundness.
	Suppose $\PSampstar$ is a cheating prover that sends some $\sigma$ to the verifier. \Ethan{on inputs x, eps, lambda...}

@@

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $m+1$-fold tensor products of identical copies of some states $\tau_j$.
	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$ \Ethan{Make that size another variable}:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{6T}{\varepsilon}\right)}{M-m}}
	\leq\frac{\varepsilon}{6}$$
	where $\sigma'_{\leq m+1}$ is the first $m+1$ registers of $\sigma'$.
	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
	$\Lambda_{m+1}$ measures the data register under the standard basis.

	We now analyze the verifier's output for each $\tau_j$ in $\rho=\sum_j w_j\tau_j^{\otimes m+1}$. Let $(d_j, z_j)$ be the verifier's output corresponding to $\tau_j$, and define $z_{j, ideal}$ accordingly.
	We claim that $\norm{(d_j, z_j)-(d_j, z_{j, ideal})}_{TV}<\frac{2\varepsilon}{6}$.
	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider the following two cases.

@@

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\frac{\varepsilon^2}{36}.$$
	which in turn implies a lower bound on the respective trace distance:
	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\varepsilon}{6}.$$
	Observe that when $d_j=\Acc$, $z_j$ is the measurement results on $\tau_j$'s data register,
	which is $\frac{\varepsilon}{6}$-close to that of $\ket{\psi_{C'(x)}}$.
	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has at least $1-\frac{\varepsilon}{6}$ probability to contain $C(x)$ due to the padding.
	So $z_j$ is $\frac{2\varepsilon}{6}$-close to $z_{ideal}$ when $d=\Acc$,
	which implies that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.

    Finally, let $(d_\rho, z_\rho)$ denote the verifier's output distribution corresponding to $\rho=\sum_j w_j\tau_j^{\otimes m+1}$,
	and define $z_{\rho, ideal}$ accordingly.
	We have $\norm{(d_\rho, z_\rho) - (d, z_{\rho, ideal})}_{TV} < \frac{2\varepsilon}{6}$ since the same is true for all components $\tau_j$.

	As $(d, z)$ is $\frac{\varepsilon}{6}$-close to $(d_\rho, z_\rho)$ by the data processing inequality,
	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
	Hence we have $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z_{\rho, ideal}) - (d, z_{ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
	The conclusion then follows from triangle inequality.
\end{prf}

### 2020-04-11 qpip0.tex
Add discussion notes

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}
\begin{enumerate}
%    \item Verifier start with description of quantum circuit $C$, input string $x$ 
    \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
    \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications. The copies have separate $\{h\}$, $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.  The verifier draws $\{h\}$ independently from the distribution specifier by step~\ref{} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round. On the second round, for each copy, the prover choose the state specified by step~\ref{} of Protocol~\ref{ProtoQPIP1}  (with  $(C,x,\eps)$ as input) as $\rho$. On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies, i.e. $c_i=1$ and $c_j=0$ for all $j\neq i$.
    \item \label{step:multi-testing}Verifier rejects if the result on any of the test rounds is rejected. 
    \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
\end{enumerate}
\end{protocol}

@@

@@

 For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,

@@

Now we are ready to prove Theorem~\ref{thm:qpip0}
\begin{proof}
We begin by considering the state $\ket{\psi}$ the prover in Protocol~\ref{proto:QPIP0samp} hold before he receives $\{c\}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.

@@

where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.

@@

%Prove that $z_{good}$ is binding.
We now proceeds to prove that $z_{good}$ is binding. I.e. there exist a $n$-qubit quantum state $\rho$ such that $z_{good}$ is $\eps$-Q-computationally indistinguishable to $\sum_z \proj{z} \tr\L(\rho \sigma_h \R)$.
\hannote{add notation for pauli matrix $\sigma_h$.}

\hannote{$\rho$ is sub normalized}

@@

>>>>

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}
Inputs: 
 Both verifier and prover start with the description of number of qubits $n$,  input string $x$ to the $\SampBQP$ Instance, and a soundness parameter $\varepsilon$.

Protocol:
\begin{enumerate}
%    \item Verifier start with description of quantum circuit $C$, input string $x$

    \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications. The copies have separate $\{h\}$, $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.  The verifier draws $\{h\}$ independently from the distribution specifier by step~\ref{step:qpip1-verify} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round. On the second round, for each copy, the prover choose the state specified by step~\ref{step:qpip1-state-gen} of Protocol~\ref{ProtoQPIP1}  (with  $(C,x,\eps)$ as input) as $\rho$. On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies, i.e. $c_i=1$ and $c_j=0$ for all $j\neq i$.
    \item \label{step:multi-testing}Verifier rejects if the result on any of the test rounds is rejected. 
    \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
\end{enumerate}
\end{protocol}

@@

\hannote{Intuitions about the partition lemma. }

@@

 For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,  \hannote{$\psi$ should not be pure state?} \hannote{actually need to fix a $pk$ for everything here.}

@@

Now we are ready to prove Theorem~\ref{thm:qpip0}
\begin{proof}
Completeness is trivial.

For soundness, We begin by considering the state $\ket{\psi}$ the prover in Protocol~\ref{proto:QPIP0samp} hold before he receives $\{c\}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.

@@

where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$. %\hannote{Note that the prover's state is actually a mixed state. In particular, $\ket{\psi}$ depends on $pk$ and we are considering the mixed state averaged over verifier's choice of $pk$.}

@@

%Prove that $z_{good}$ is binding.
We now proceeds to prove that $z_{good}$ is binding. I.e. there exist a subnormalized $n$-qubit quantum state $\rho_{good}$ such that $z_{good}$ is $\eps$-Q-computationally indistinguishable to $M_{XZ}(\rho_{good},h)$.

\hannote{$M_{XZ}(\rho_{good},h)=\sum_z \proj{z} \tr\L(\rho \sigma_{h,z} \R)?$}.
\hannote{add notation for pauli matrix $\sigma_h$.}

@@

For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}: The prover tries to run $U_0$ by taking the verifier's input as $i$-th copy of protocol~\ref{proto:QPIP0samp} and simulating other $m-1$ copies by himself. The prover then \hannote{picks a uniformly random $\gamma$ ?}  tries to generate $\ket{\psi_{1^{i-1}1,\gamma}}$ by applying $G_{i,1,\gamma}G_{i-1,1,\gamma} \cdots G_{2,1,\gamma}G_{1,1,\gamma}$. If the prover fails to generate $\ket{\psi_{1^{i-1}1,\gamma}}$, he throws out everything and run $U_{trivial,0}$ described  in  Lemma~\ref{lem:trivial-4-round-strategy} instead. This is possible because all the inputs are classical. On the fourth round, if the prover had generated $\ket{\psi_{1^{i-1}1,\gamma}}$, he reply with the $i$-th register of $\ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)$, where $\ext_i$ is specified in property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}. otherwise he continues to run the strategy of Lemma~\ref{lem:trivial-4-round-strategy}. We denote the random variable the verifier would get on the testing round as $z_{construct}$.

==== old ===
